---
title: "Publications"
format: html
execute:
  echo: false
  warning: false
  message: false
---

My publication list is pulled automatically from my [Google Scholar profile](https://scholar.google.com/citations?hl=en&user=isfLoMsAAAAJ) using R. If you are interested in an article that is not Open Access, please [reach out](mailto:mduma060@uottawa.ca).

The data and code used for my publications are archived on my [Open Science Framework page](https://osf.io/e3v68/).

```{r, include = FALSE}
library(scholar)
library(tidyverse)
library(glue)
library(gt)

# escape some special chars, german umlauts, ...
char2html <- function(x) {
  dictionary <- data.frame(
    symbol = c("Ă¤", "Ă¶", "Ă¼", "Ă„", "Ă–", "Ăœ", "ĂŸ"),
    html = c(
      "&auml;", "&ouml;", "&uuml;", "&Auml;",
      "&Ouml;", "&Uuml;", "&szlig;"
    )
  )
  for (i in 1:dim(dictionary)[1]) {
    x <- gsub(dictionary$symbol[i], dictionary$html[i], x)
  }
  x
}

# my google scholar user id from my profile url
# https://scholar.google.com/citations?hl=en&user=isfLoMsAAAAJ
id_mnd <- "isfLoMsAAAAJ"

```

Researcher h-index: `r get_profile(id_mnd)$h_index`

Total number of citations: `r get_profile(id_mnd)$total_cites`

```{r, echo = FALSE}

# pull from google
pubs <- get_publications(id_mnd)

for (x in 1:length(pubs$pubid)) {
  var_pubid <- pubs$pubid[x]
  pubs$pub_url[x] <- get_publication_url(id = id_mnd, pub_id = var_pubid)
}

# create a formatted citation
pubs <- pubs %>%
  arrange(desc(year)) %>%
  mutate(citation = glue('{author}. ({year}) {title}, {journal}, {number}. {pub_url}  [citations: {cites}].')) %>%
  group_by(year) %>%
  mutate(pub_number = row_number()) %>%
  ungroup()

# print nicely as HTML

for (yr in unique(pubs$year)) {
  cat(glue("<h3>{yr}</h3>\n"))
 
  pubs_year <- pubs %>% filter(year == yr)
  
  cat("<ol>\n")  # start numbered list
  for (i in 1:nrow(pubs_year)) {
    cat(glue(
      '<li>{pubs_year$author[i]} ({pubs_year$year[i]}) <a href="{pubs_year$pub_url[i]}" target="_blank">{pubs_year$title[i]}</a>, *{pubs_year$journal[i]}*: {pubs_year$number[i]}. [citations: {pubs_year$cites[i]}]</li>\n'
    ))
  }
  cat("</ol>\n\n")
}

```
