---
title: "Publications"
---

My publication list is pulled automatically from my [Google Scholar profile]("https://scholar.google.com/citations?hl=en&user=isfLoMsAAAAJ") using R. If you are interested in an article that is not Open Access, please [reach out](mailto:mduma060@uottawa.ca)

The data and code used for my publications are archived on my [Open Science Framework page]("https://osf.io/e3v68/").

PAGE UNDER CONSTRUCTION

```{r, include = FALSE}
library(scholar)
library(tidyverse)
library(glue)
library(gt)

# escape some special chars, german umlauts, ...
char2html <- function(x) {
  dictionary <- data.frame(
    symbol = c("ä", "ö", "ü", "Ä", "Ö", "Ü", "ß"),
    html = c(
      "&auml;", "&ouml;", "&uuml;", "&Auml;",
      "&Ouml;", "&Uuml;", "&szlig;"
    )
  )
  for (i in 1:dim(dictionary)[1]) {
    x <- gsub(dictionary$symbol[i], dictionary$html[i], x)
  }
  x
}

# my google scholar user id from my profile url
# https://scholar.google.com/citations?hl=en&user=isfLoMsAAAAJ
id_mnd <- "isfLoMsAAAAJ"

```

Researcher h-index: `r get_profile(id_mnd)$h_index`

Total number of citations: `r get_profile(id_mnd)$total_cites`

```{r, echo = FALSE}

# pull from google
pubs <- get_publications(id_mnd)

for (x in 1:length(pubs$pubid)) {
  var_pubid <- pubs$pubid[x]
  pubs$pub_url[x] <- get_publication_url(id = id_mnd, pub_id = var_pubid)
}

# formating
pubs <- pubs %>%
  arrange(desc(year)) %>%
  split(.$year) %>%
  map(function(x) {
    x <- x %>%
      glue_data('{author}. ({year}). {title}, {journal}, {number}. [citations: {cites}].')

    return(x)
  }) %>%
  rev()
  
pubs

```
